---
title: "Write up Linear Model"
author: "Rashonda Weathersby"
date: "3/23/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

You can import the data directly from a link to its website.  Copy that link to the clipboard by right clicking on Raw Data and then copy link.


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```


```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  
```


```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
```
##Now add in scatterplot

```{r}
basicNN + geom_point()
```
  
The plot value of SIMS and ARM.
# Numerical results

```{r}
cor(SIMS~ARM,data=data)
```

# Inferential  (Build linear model)
  
```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```


The equation for Sims explained by Arm is 
Sim -4.1 + .054563 * ARM


```{r}
newdata=data.frame(GRIP=94,ARM=88)
predict(model.1 ,newdata,interval ="prediction")
```
The newdata interval shows the prediction of Grip 94,and Arm 88.

# now add the model fit to our plot
  
```{r}
basicNN + geom_point(aes(y=SIMS,x=ARM)) + geom_smooth(method=lm)
``` 



The line represents a 95% confidence value. 


```{r}
basicGG<- ggplot(data,aes(y=SIMS,x=GRIP))
```
##Now add in scatterplot

```{r}
basicGG + geom_point()
```
This boxplot shows the value of SIMS= Grip.   

# Numerical results

```{r}
cor(SIMS~GRIP,data=data)
```
The grip numerical value 0.6398458.

# Inferential  (Build linear model)
  
```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
predict(model.2 ,newdata,interval ="prediction")
```
Sim -4.8 + .0.0454 * GRIP
 
# now add the model fit to our plot
  
```{r}
basicGG + geom_point(aes(y=SIMS,x=GRIP)) + geom_smooth(method=lm)
``` 

The equation for Sims explained by GRIP is 
Sim -4.8 + .0.0454 * GRIP

```{r}
model.3 <- lm(SIMS~ ARM+GRIP,data=data)
summary.lm(model.3)
predict(model.3 ,newdata,interval ="prediction")
```
SIMS= -5.434 + 0.373* ARM + 0.0244*GRIP

```{r}
anova(model.1,model.3)
```
We reject the null hypothesis, due to the p-value being so small. We come to the conclusion that model 3 is the biggest adjusted r squared, which makes it the best. 
